An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-05-10 poly-embed-journal/poly-embed-journal.tex
Cleaning up Prop 2

\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}

@@

    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
    \jessie{Skip and go to orange for now.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead. -21 Mar 21}

  \raft{Good start.  Let's take it a bit slower.  I was thinking you start with the facets, which by definition have interiors.  Then pick a point *of the graph*, one on the interior of each facet.  Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.  Now you can define $S$ (all the $r$'s you just gathered).  The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.  And so on.}
  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
  Form $S$ by taking one such report for each facet.}
  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.

\proposedadd{ALTERNATE PROOF FOR REVERSE IMPLICATION: 
	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
	Construct $\Sc := \Sc(\ell)$ as in Definition~\ref{cons:rep-set}, and $\U := \Sc(L)$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
	Such an embedding is well-defined as the facets are the same since the risks are equal.
	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.
}

\proposedadd{To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
Matching optimality is true by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.}\jessie{This feels like it's missing a detail about how $\Sc$ is minimal.}
\end{proof}

@@

\begin{proposition}\label{prop:trim-unique}
	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[Trim]\label{def:trim-loss}
	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{proposition}\label{prop:trim-loss-condition}
	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{proposition}
\begin{proof}[Sketch]
	Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.

	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.

	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.

	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
	Let the discrete loss $\ell$ be given.
	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
	$\implies$
	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
	$\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
	By Proposition~\ref{prop:trim-unique}, we have
	\begin{equation*}
	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
	\end{equation*}
	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

	$\impliedby$
	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
	As these losses match we trivially have the second embedding condition matching losses.
	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\begin{align*}
	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
	\end{align*}
\end{proof}

As we define one loss embedding another, one can imagine an analagous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.

\jessie{Just took old TFAE for now, but this is quite different from Prop 4, united by (c) in each}
\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
		\item \jessie{Adding} $\R^*$ is a finite (minimum?) representative set for $\Gamma$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	Moreover, when any of the above hold, $\trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}

>>>>

\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

@@

    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}

% commented out 10 May 21 to consolidate/clean/switch to proof relying on supporting hyperplanes of Bayes Risks
%    \jessie{Skip and go to orange for now.}
%  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
%  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
%  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
%  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
%  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead. -21 Mar 21}

% commented out 10 May to consolidate/clean
%  \raft{Good start.  Let's take it a bit slower.  I was thinking you start with the facets, which by definition have interiors.  Then pick a point *of the graph*, one on the interior of each facet.  Then observe it must come from some $r$ and $p$, i.e., $(p,\inprod{p}{\ell(r)})$.  Now you can define $S$ (all the $r$'s you just gathered).  The embedding comes next, using the Bayes risk matching to get that same graph point written as $(p,\inprod{p}{L(u)})$: define $\varphi(r) = u$ for that $r$ and $u$.  And so on.}
%  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
%  Form $S$ by taking one such report for each facet.}
%  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
%  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
%  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
%  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
%  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
%  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
	Construct $\Sc := \Sc(\ell)$ as in Definition~\ref{cons:rep-set}, and $\U := \Sc(L)$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
	Such an embedding is well-defined as the facets are the same since the risks are equal.
	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.

We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
\end{proof}

@@

\begin{proposition}\label{prop:trim-unique}
	Suppose $\R$ and $\R'$ are finite minimum representative sets for the loss $L$.
	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[Trim]\label{def:trim-loss}
	Given a loss $L:\R \to \reals_+^\Y$ with a finite representative set, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{corollary}\label{prop:trim-loss-condition}
	Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $R^*$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{corollary}
\begin{proof}[Sketch]
	Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
	The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimal representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.

%commented out 06 May 21	
%	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.
%	
%	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
%	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.
%	
%	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
%	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
%	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
%	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
%	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
	Let the discrete loss $\ell$ be given.
	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
	Moreover, when $\trim(L) = \trim(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$. \jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
	$\implies$
	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
	$\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
	By Proposition~\ref{prop:trim-unique}, we have
	\begin{equation*}
	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
	\end{equation*}
	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

	$\impliedby$
	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
	As these losses match we trivially have the second embedding condition matching losses.
	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\begin{align*}
	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
	\end{align*}

	Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(\ell) = \trim(\ell|_{\R^*})$ and $\ell|_{\R^*}$ is non-redundant.
	Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
\end{proof}

As we define one loss embedding another, one can imagine an analogous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.

\begin{remark}\label{remark:embed-trim}
	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
		\item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
		\item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
	\end{enumerate}
Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ has no duplicate elements such that $\cup \Theta' = \simplex$.
\end{remark}
\begin{proof}[Sketch]
	$(a \implies b)$
	If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.

	$(b \implies c)$
	Consider that if $\U$ is a finite representative set for $L$, then $L$ has a finite minimum representative set $\U' \subseteq \U$.
	We have $\Theta := \trim(\Gamma) = \{\Gamma_u \mid u \in \U'\}$.
	This is finite as $\U'$ is finite, and unions to the simplex by $\U'$ being representative.
	If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

	$(c \implies a)$ 
	For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\U'$ to be the set of such $u$s.
	We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and therefore we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.

%tight version; commented out May 8, 2021
%$(a \implies b)$
%If $\Gamma$ tightly embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite minimum representative set for $L$.
%We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$.
%If $\U$ was not minimum, then there would be some $r \in \R'$ so that $\U \setminus \{\varphi(r)\}$ is still representative.
%This is true if and only if $\R' \setminus \{r\}$ is still representative for $\ell$, which contradicts non-redundancy of $\ell$ by tight embedding (Prop~\ref{prop:tfae-min-rep-nonredundant}).
%Therefore, $\U$ is a finite minimum representative set for $L$.
%
%$(b \implies c)$
%We have $\trim(\Gamma) = \{\Gamma_u \mid u \in \varphi(\R')\}$, and take $\Theta := \trim(\Gamma)$.
%This is finite as $\varphi(\R')$ is finite, and unions to the simplex by $\varphi(\R')$ being representative.
%If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}
%
%
%$(c \implies a)$ \jessie{Not quite: we need the multiset to have no duplicate elements}
%%If we show $ c \implies b$, we have $b \implies a$ as an version of Corollary~\ref{cor:representative-embeds-restriction}.
%For each $\theta \in \Theta$, there is some $u \in \R$ so that $\theta = \Gamma_u$; take $\R'$ to be the set of such $u$s.
%If $\R'$ is a minimum representative set, then we have the result by an analog of Corollary~\ref{cor:representative-embeds-restriction}.
%
%We can see $\R'$ is representative since $\cup_{u \in \R'} \Gamma_u = \cup \theta = \simplex$, and it is minimum since the multiset of $\Theta$ has no duplicate elements.
%As the level sets are full-dimensional, each level set $\Gamma_u$ has some $p_u$ such that $\Gamma(p_u) = \{u\}$, so removing any $u$ from $\R'$ would make $\R'$ not representative.	
\end{proof}
